Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-05-02 article.rnw
Add the grouped matrix module, and required LaTeX packages, to article.rnw.

%Images
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{colortbl}

@@

<<include=FALSE>>=
	source("r/input-data.R")
	source("r/post-process.R")
	source("r/brute-post-process.R")
	source("r/mantel-test.R")
	source("r/dist-matrix.R")
	source("r/coclassification-table.R")

>>>>

%Images & tables
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{colortbl}
\usepackage{multirow}
\usepackage{arydshln}

@@

<<include=FALSE>>=
	source("r/parameters.R")
	source("r/input-data.R")
	source("r/post-process.R")
	source("r/brute-post-process.R")
	source("r/mantel-test.R")
	source("r/dist-matrix.R")
	source("r/coclassification-table.R")
	source("r/grouped-matrix.R")
